---
title: "Ratings Transfer Summary"

output: html_document
---
```{r, echo=FALSE, results="hide"}
source('analysis.R') # sources the analysis and functions for this project
source('R/functions.R')
library(ggplot2)
```


**N = `r length(participant)`**

**Ratings on a scale of -10 - + 10**

- -10: Cue perfectly prevents outcome delivery
- 0: No relationship between cue and outcome delivery or non-delivery
- +10: Cue perfectly predicts outcome delivery

###Causal Ratings of Trained Cues

```{r, echo = FALSE}
oldcues_graph
```

#### Summary Data

```{r, echo = FALSE}
model.tables(old.rating.aov, "means")
```

#### Summary Statistics

```{r, echo = FALSE}
summary(old.rating.aov)
```


### Causal Ratings of Novel Cues
```{r, echo = FALSE}
novelcues_graph
```

#### Summary Data

#### Summary Statistics

```{r, echo = FALSE}
pairedTTest(novel.same, novel.diff)
```

**Rated relationship of Excitor to Same Outcome**

```{r, echo = FALSE}
t.test(novel.same, mu = 0)
```

**Rated relationship of Excitor to Different Outcome**
```{r, echo = FALSE}
t.test(novel.diff, mu = 0)
```

### Causal Ratings of Novel Compound Cues

```{r, echo = FALSE}
transfercues_graph
```


#### Summary Data

```{r, echo = FALSE}
model.tables(transfer.rating.aov, "means")
```


#### Summary Statistics 

```{r, echo = FALSE}
summary(transfer.rating.aov)
```

